Data prep for Shiny app

### 2017-04-21 case_study_mpa/1_wdpa_poly_to_raster.Rmd
initialize dummy branch

``` {r rasterize_that_shit}
dir_rast <- file.path(dir_anx, 'explore_am_v_iucn/mpa_rasters')

@@

### import WDPA database polygons from saved .shp
dir_rast <- file.path(dir_anx, 'explore_am_v_iucn/mpa_rasters')
dir_wdpa   <- file.path(dir_rast, 'WDPA2014_mar_klein')
lyr_wdpa    <- 'wdpa_all_mar_klein'
lyr_mpa     <- 'wdpa_all_mar_klein_i-iv'

>>>>

``` {r rasterize_that_shit}
dir_rast <- file.path(dir_anx, 'vAM_IUCN/mpa_rasters')

@@

### import WDPA database polygons from saved .shp
dir_rast <- file.path(dir_anx, 'vAM_IUCN/mpa_rasters')
dir_wdpa   <- file.path(dir_rast, 'WDPA2014_mar_klein')
lyr_wdpa    <- 'wdpa_all_mar_klein'
lyr_mpa     <- 'wdpa_all_mar_klein_i-iv'

### 2017-04-21 case_study_mpa/2_wdpa_rast_to_csv.Rmd
initialize dummy branch

dir_rast <- file.path(dir_anx, 'explore_am_v_iucn/mpa_rasters')
rast_mpa_mar_file <- file.path(dir_rast, 'rast_mpa_mar_i-iv.tif')
# rast_mpa_mar_file <- file.path(dir_rast, 'wdpa_all_mar_klein_i-iv.tif')
rast_mar_file <- file.path(dir_rast, 'rast_marine.tif')

>>>>

dir_rast <- file.path(dir_anx, 'vAM_IUCN/mpa_rasters')
rast_mpa_mar_file <- file.path(dir_rast, 'rast_mpa_mar_i-iv.tif')
# rast_mpa_mar_file <- file.path(dir_rast, 'wdpa_all_mar_klein_i-iv.tif')
rast_mar_file <- file.path(dir_rast, 'rast_marine.tif')

### 2017-04-21 clip_depth/coral_maps.Rmd
initialize dummy branch

@@

quad_names <- data.frame('quad' = c('q1', 'q2', 'q3', 'q4'),
                         'quad_name' = factor(c('well-aligned', 'dist-aligned', 
                                                'area-aligned', 'poorly aligned'),
                                             ordered = TRUE))

iucn_coral_quads <- iucn_coral_quads %>%
  left_join(quad_names, by = 'quad')

write_csv(iucn_coral_quads, file.path(dir_git, 'clip_depth', 'iucn_coral_quads.csv'))

@@

iucn_coral_quad_sum <- read_csv(file.path(dir_git, 'clip_depth', 'iucn_coral_quads.csv')) %>%
  dplyr::select(method, quad, quad_name, pct_quad) %>%
  distinct()
### Plot the bar chart
barchart_coral_quads <- ggplot(iucn_coral_quad_sum, 
                                aes(x = method, fill = quad, weight = pct_quad)) +
  theme(panel.grid.major.y = element_blank()) +
  geom_bar(stat = 'count', alpha = 1) +
  scale_fill_manual(values = c('q4' = '#d01c8b', 
                               'q3' = '#f1b6da', 
                               'q2' = '#b8e186',
                               'q1' = '#4dac26'),
                    labels = quad_names$quad_name) +
  scale_y_continuous(expand = c(0, 0), 
                     limits = c(0, 1),
                     breaks = break_nums/100,
                     labels = sprintf('%s%%', break_nums)) + 
  ### add grid lines; horizontal but then get flipped
  geom_hline(yintercept = break_nums/100, size = 0.25, color = 'white', alpha = .5) +
  coord_flip() +
  labs(x = 'Depth limit', 
       y = 'Percent of corals by quadrant', 
       fill = 'Alignment')

>>>>

ggsave(plot = clipped_quads,
       filename = file.path(dir_fig, 'si_scatter_quadmap_corals.tif'), device = 'tiff',
       width = 19, height = 9, units = 'cm', dpi = 600)

@@

quad_names <- data.frame('quad' = c('q4', 'q3', 'q2', 'q1'),
                         'quad_name' = factor(c('poorly aligned', 
                                                'area-aligned', 
                                                'dist-aligned',
                                                'well-aligned'),
                                             ordered = TRUE))

iucn_coral_quads1 <- iucn_coral_quads %>%
  left_join(quad_names, by = 'quad') %>%
  mutate(quad = factor(quad, levels = c('q4', 'q3', 'q2', 'q1'), ordered = TRUE))

write_csv(iucn_coral_quads1, file.path(dir_git, 'clip_depth', 'iucn_coral_quads.csv'))

@@

iucn_coral_quad_sum <- iucn_coral_quads1 %>%
  dplyr::select(method, quad, quad_name, pct_quad) %>%
  distinct()
### Plot the bar chart
barchart_coral_quads <- ggplot(iucn_coral_quad_sum, 
                                aes(x = method, fill = quad, weight = pct_quad)) +
  theme(panel.grid.major.y = element_blank()) +
  geom_bar(stat = 'count', alpha = 1) +
  scale_fill_manual(values = c('q4' = '#d01c8b', 
                               'q3' = '#f1b6da', 
                               'q2' = '#b8e186',
                               'q1' = '#4dac26'),
                    labels = quad_names$quad_name,
                    guide = guide_legend(reverse = TRUE)) +
  scale_y_continuous(expand = c(0, 0), 
                     limits = c(0, 1),
                     breaks = break_nums/100,
                     labels = sprintf('%s%%', break_nums)) + 
  ### add grid lines; horizontal but then get flipped
  geom_hline(yintercept = break_nums/100, size = 0.25, color = 'white', alpha = .5) +
  coord_flip() +
  labs(x = 'Depth limit', 
       y = 'Percent of corals by quadrant', 
       fill = 'Alignment')

### 2017-04-21 data_explore/data_explore.Rmd
initialize dummy branch

bar_taxa <- ggplot(taxa_df2, aes(x = class, color = dataset)) +
  theme(panel.grid.major.x = element_blank(),
        axis.text.x  = element_text(angle = 75, hjust = 1),
        axis.title.y = element_text(hjust = 0)) +
  geom_linerange(aes(ymin = start, ymax = end, size = dataset),
                 position = position_dodge(width = 0.5)) +
  scale_size_manual(values = c('IUCN' = .5, 'AquaMaps' = .5, 'Paired' = 2.6)) +
  scale_color_manual(values = c('IUCN' = 'black', 'AquaMaps' = 'grey70', 'Paired' = 'black')) +
  geom_text(aes(label = n_label, y = 102),
            size = 2.4,
            angle = 90,
            hjust = 0,
            color = 'grey30') +
  scale_y_continuous(expand = c(0, 0),
                     limits = c(0, 140),
                     breaks = break_nums,
                     labels = sprintf('%s%%', break_nums)) +
  labs(x = 'Class (in order of decreasing number of included species)',
       y = '% of mapped species',
       fill = 'Dataset')

print(bar_taxa)
ggsave(filename = file.path(dir_fig, 'bar_by_taxa_all.png'), 
       width = 19.05, height = 7, units = 'cm', dpi = 600)

>>>>

bar_taxa <- ggplot(taxa_df2, aes(x = class, color = dataset)) +
  ggtheme_basic() +
  theme(panel.grid.major.x = element_blank(),
        axis.text.x  = element_text(angle = 75, hjust = 1),
        axis.title.y = element_text(hjust = 0)) +
  geom_linerange(aes(ymin = start, ymax = end, size = dataset),
                 position = position_dodge(width = 0.5)) +
  scale_size_manual(values = c('IUCN' = .5, 'AquaMaps' = .5, 'Paired' = 2.6)) +
  scale_color_manual(values = c('IUCN' = 'black', 'AquaMaps' = 'grey70', 'Paired' = 'black')) +
  geom_text(aes(label = n_label, y = 102),
            size = 2.4,
            angle = 90,
            hjust = 0,
            color = 'grey30') +
  scale_y_continuous(expand = c(0, 0),
                     limits = c(0, 140),
                     breaks = break_nums,
                     labels = sprintf('%s%%', break_nums)) +
  labs(x = 'Class (in order of decreasing number of included species)',
       y = '% of mapped species',
       fill = 'Dataset')

print(bar_taxa)
# ggsave(filename = file.path(dir_fig, 'bar_by_taxa_all.png'), 
#        width = 19.05, height = 7, units = 'cm', dpi = 600)

### 2017-04-21 data_explore/data_explore_global_maps.Rmd
initialize dummy branch

all_am_rast_file   <- file.path(dir_data, 'rasters/am_all_rast.tif')
dir_am_data <- file.path(dir_N, 'git-annex/globalprep/_raw_data/aquamaps/v2015/csv')

@@

png(file.path(dir_fig, 'all_aquamaps_map.png'),
    width = 8.7, height = 6, units = 'in', res = 300)
print(am_levelplot1)
dev.off()

@@

all_iucn_rast_file   <- file.path(dir_data, 'rasters/iucn_all_rast.tif')
dir_data_iucn <- file.path(dir_N, 'git-annex/globalprep/_raw_data/iucn_spp')

@@

png(file.path(dir_fig, 'all_iucn_map.png'),
    width = 8.7, height = 6, units = 'in', res = 300)
print(iucn_levelplot1)
dev.off()

>>>>

all_am_rast_file   <- file.path(dir_data, 'rasters/am_all_rast.tif')
dir_am_data <- file.path(dir_M, 'git-annex/globalprep/_raw_data/aquamaps/d2015/csv')

@@

png(file.path(dir_fig, 'all_aquamaps_map.png'),
    width = 8.7, height = 6, units = 'cm', res = 600)
print(am_levelplot1)
dev.off()

@@

all_iucn_rast_file   <- file.path(dir_data, 'rasters/iucn_all_rast.tif')
dir_data_iucn <- file.path(dir_M, 'git-annex/globalprep/_raw_data/iucn_spp')

@@

png(file.path(dir_fig, 'all_iucn_map.png'),
    width = 8.7, height = 6, units = 'cm', res = 600)
print(iucn_levelplot1)
dev.off()

### 2017-04-21 data_explore/data_explore_quadmaps.Rmd
initialize dummy branch

for (i in 1:length(spp_quads)) { # i = 1
  species = spp_quads[i]

@@

  if (i == 1) {
    spp_map <- tm_shape(spp_rast) +
      tm_raster(palette = c('#4dac26', '#d01c8b', '#88ccff'),
                title  = 'Dataset',
                labels = c('AquaMaps', 'IUCN', 'both'),
                colorNA = '#f0f8ff',
                showNA = FALSE,
                alpha = .8)
  } else {
    spp_map <- tm_shape(spp_rast) +
      tm_raster(palette = c('#4dac26', '#d01c8b', '#aaccff'),
                legend.show = FALSE,
                colorNA = '#f0f8ff',
                alpha = .8)
  }

  spp_map <- spp_map +
    tm_shape(fao_polys_crop) +
      tm_borders(col = 'grey70', lwd = 0.25, alpha = .3) +
    tm_shape(world_crop) +
      tm_polygons(border.col = 'grey45', col = 'grey40', lwd = 0.25) + 
    tm_layout(# title = species, title.size = .75,
              # title.position = c('left', 'bottom'),
              frame = FALSE,
              legend.text.size = .6,
              legend.title.size = .7,
              legend.outside = FALSE,
              legend.position = c('right', 'bottom'),
              legend.bg.color = '#f0f8ff',
              legend.bg.alpha = .9,
              attr.outside = TRUE)

>>>>

for (i in 1:length(spp_quads)) { # i = 3
  species = spp_quads[i]

@@

  if (i == 1) {
    spp_map <- tm_shape(spp_rast) +
      # tm_raster(palette = c('#8da0cb', '#fc8d62', '#66c2a5'),
      tm_raster(palette = c('#660000', 'yellowgreen', 'firebrick1'),
                title  = 'Dataset',
                labels = c('AquaMaps', 'IUCN', 'both'),
                colorNA = '#f0f8ff',
                showNA = FALSE,
                alpha = .8)
  } else {
    spp_map <- tm_shape(spp_rast) +
      tm_raster(palette = c('#660000', 'yellowgreen', 'firebrick1'),
                legend.show = FALSE,
                colorNA = '#f0f8ff',
                alpha = .8)
  }

  spp_map <- spp_map +
    tm_shape(fao_polys_crop) +
      tm_borders(col = 'grey70', lwd = 0.25, alpha = .3) +
    tm_shape(world_crop) +
      tm_polygons(border.col = 'grey50', col = 'grey40', lwd = 0.25) + 
    tm_layout(# title = species, title.size = .75,
              # title.position = c('left', 'bottom'),
              frame = FALSE,
              legend.text.size = .6,
              legend.title.size = .7,
              legend.outside = FALSE,
              legend.position = c('right', 'bottom'),
              legend.bg.color = '#f0f8ff',
              legend.bg.alpha = .9,
              attr.outside = TRUE)

### 2017-04-21 data_explore/data_prep.Rmd
initialize dummy branch

```{r verify_spp_names_in_shps, echo = FALSE, warning = FALSE, message = FALSE, eval = FALSE}

@@

@@

spp_am_v_iucn <- spp_all %>%
  select(-iucn_subpop) %>%
  filter(!is.na(iucn_sid) & !is.na(am_sid)) %>%
  unique()

# length(unique(spp_am_v_iucn$sciname)); length(unique(spp_am_v_iucn$am_sid)); length(unique(spp_am_v_iucn$iucn_sid))
### NOTE: 2332 unique scientific names, unique am_sid and unique iucn_sid.
### Seasnakes are included in Reptiles (IUCN).  Two "mangroves" that are actually seagrasses.
spp_am_v_iucn <- spp_am_v_iucn %>%
  group_by(am_sid, iucn_sid) %>%
  mutate(dupes = n() - 1) %>%
  ungroup() %>%
  filter(!(dupes == 1 & spp_group == 'MANGROVES')) %>%
  filter(spp_group != 'SEASNAKES') %>%
  select(-dupes)
# length(unique(spp_am_v_iucn$sciname)); length(unique(spp_am_v_iucn$am_sid)); length(unique(spp_am_v_iucn$iucn_sid))
### still same scinames and am_sid

sciname_dupes <- spp_am_v_iucn %>%
  group_by(sciname) %>%
  filter(n() > 1)
### these seem to be spp with IUCN maps for synonyms.  Keep 'em in.

@@

spp_all <- read_csv(file.path(dir_data, 'spp_all.csv'))

# library(rgbif)

# system.time({
#   x <- occ_search(scientificName = spp_all$sciname[1:100], fields = 'minimal', limit = 1)
#   ### seems linear - 10 names ~ 2.5 sec, 100 names ~ 25 sec, 1000 names, ~250 sec
#   ### so 30000 names ~ 7500 sec or 2 hours
# })
# y <- sapply(x, function(x) x$meta$count)
# gbif_occur <- data.frame(sciname = names(y), gbif_occ = y)
# 
# gbif_occur <- gbif_occur %>% 
#   left_join(spp_all %>%
#               select(iucn_sid, am_sid, sciname),
#             by = 'sciname') %>%
#   left_join(read_csv(file.path(dir_data_remote, 'aquamaps/v2015/csv/speciesoccursum.csv')) %>%
#                        select(am_sid = speciesid, occurcells),
#                      by = 'am_sid')

# plot(ln_obs ~ ln_occurcells, data = gbif_occur)
# plot(obs ~ occurcells, data = gbif_occur)
# print(summary(lm(obs ~ occurcells, data = gbif_occur)))

# write_csv(gbif_occur, file.path(dir_data, 'gbif_occurrence.csv'))
gbif_occur <- read_csv(file.path(dir_data, 'gbif_occurrence.csv'))

# source('obis_count.R')
# scinames <- spp_all$sciname
# 
# obis_occur <- obis_count(scinames)
# obis_occur <- obis_count(scinames[26500:26600], verbose = TRUE)
# 
# obis_occur <- obis_occur %>% 
#   left_join(spp_all %>%
#               select(iucn_sid, am_sid, sciname),
#             by = 'sciname') %>%
#   left_join(read_csv(file.path(dir_data_remote, 'aquamaps/v2015/csv/speciesoccursum.csv')) %>%
#                        select(am_sid = speciesid, occurcells),
#                      by = 'am_sid')
# 
# write_csv(obis_occur, file.path(dir_data, 'obis_occurrence.csv'))
obis_occur <- read_csv(file.path(dir_data, 'obis_occurrence.csv'))

>>>>

```{r verify_spp_names_in_shps, echo = FALSE, warning = FALSE, message = FALSE, eval = FALSE}
### Some species names in the shapefile polygons do not match the IUCN database names.  Fix this!

@@

``` {r test_worrms_matching}

library(worrms)
spp_map_pairs <- read_csv(file.path(dir_data, 'spp_list_w_area_trimmed.csv'))

spp_names <- spp_map_pairs$sciname

iucn_maps_file <- file.path(dir_data, 'spp_iucn_maps_verified.csv')
spp_iucn_maps <- read_csv(iucn_maps_file)

spp_am_ver <- lapply(spp_am_maps$sciname, FUN = function(x) {
    y <- try(wm_records_names(x))
    if (class(y) != 'try-error') {
      return(as.data.frame(y))
    } else {
      return(data.frame(status = 'error'))
    }
  }) %>%
  setNames(spp_am_maps$sciname) %>%
  bind_rows(.id = 'sciname_orig')

spp_am_ver1 <- spp_am_maps %>%
  select(am_sid, sciname, iucn_id) %>%
  left_join(spp_am_ver %>%
    select(sciname_orig, sciname_worrms = scientificname, status, sciname_accepted = valid_name),
    by = c('sciname' = 'sciname_orig')) %>%
  distinct() %>%
  mutate(am_name_ver = sciname == sciname_accepted)

write_csv(spp_am_ver1, file.path(dir_git, 'data/sciname_lookups/am_worrms_verified.csv'))

spp_iucn_ver <- lapply(spp_iucn_maps$sciname, FUN = function(x) {
    y <- try(wm_records_names(x))
    if (class(y) != 'try-error') {
      return(as.data.frame(y))
    } else {
      return(data.frame(status = 'error'))
    }
  }) %>%
  setNames(spp_iucn_maps$sciname) %>%
  bind_rows(.id = 'sciname_orig')

spp_iucn_ver1 <- spp_iucn_maps %>%
  select(iucn_sid, sciname, spp_group) %>%
  left_join(spp_iucn_ver %>%
    select(sciname_orig, sciname_worrms = scientificname, status, sciname_accepted = valid_name),
    by = c('sciname' = 'sciname_orig')) %>%
  distinct() %>%
  mutate(iucn_name_ver = sciname == sciname_accepted)

write_csv(spp_iucn_ver1, file.path(dir_git, 'data/sciname_lookups/iucn_worrms_verified.csv'))

### match by id first
id_match <- inner_join(spp_iucn_ver1 %>%
                         select(iucn_sid, iucn_sciname = sciname, iucn_sciname_accepted = sciname_accepted), 
                       spp_am_ver1 %>%
                         select(am_sid, iucn_id, am_sciname = sciname, am_sciname_accepted = sciname_accepted),
                       by = c('iucn_sid' = 'iucn_id')) %>%
  distinct()
### 1960 matches; all distinct?
# length(id_match$iucn_sid %>% unique()); length(id_match$am_sid %>% unique())
# 1880 for both (same as prior method, which makes sense)

### then match the rest by verified accepted name
iucn_id_miss <- spp_iucn_ver1 %>%
  filter(!iucn_sid %in% id_match$iucn_sid)
am_id_miss <- spp_am_ver1 %>%
  filter(!am_sid %in% id_match$am_sid)

name_match_base <- inner_join(iucn_id_miss, am_id_miss, by = 'sciname')
# length(name_match_base$iucn_sid %>% unique()); length(name_match_base$am_sid %>% unique())
### additional 463; 452 are unique, for total of 2332, which matches old method
name_match_worms <- inner_join(iucn_id_miss %>%
                                 filter(!is.na(sciname_accepted)) %>%
                                 rename(iucn_sciname = sciname), 
                               am_id_miss %>%
                                 filter(!is.na(sciname_accepted)) %>%
                                 rename(am_sciname = sciname), 
                               by = 'sciname_accepted') %>%
  filter(status.x != 'unaccepted' & status.y != 'unaccepted') ### both unaccepted? too much uncertainty - eliminate

# length(name_match_worms$iucn_sid %>% unique()); length(name_match_worms$am_sid %>% unique())
### additional 480; 467 IUCN are unique, and 464 AquaMaps, for total of 2332, which makes sense
worms_no_basename <- name_match_worms %>%
  filter(!iucn_sid %in% name_match_base$iucn_sid) %>%
  select(iucn_sid, am_sid, sciname = sciname_accepted)
### matched by WoRMS names but not by basic names from original databases

basename_no_worms <- name_match_base %>%
  filter(!am_sid %in% name_match_worms$am_sid) %>%
  select(iucn_sid, am_sid, sciname)
### these are all ones with no WoRMS match for either database, but matched by original names

id_match_cleaned <- id_match %>%
  select(iucn_sid, am_sid, sciname = iucn_sciname) %>%
  distinct()

species_id_lookup <- id_match_cleaned %>%
  mutate(match = 'id') %>%
  bind_rows(name_match_base %>%
              select(iucn_sid, am_sid, sciname) %>%
              mutate(match = 'basic name')) %>%
  bind_rows(worms_no_basename %>%
              mutate(match = 'worms')) %>%
  distinct()

### 2351 species on the list
x <- species_id_lookup %>%
  filter(iucn_sid %in% species_id_lookup$iucn_sid[duplicated(species_id_lookup$iucn_sid)])
y <- species_id_lookup %>%
  filter(am_sid %in% species_id_lookup$am_sid[duplicated(species_id_lookup$am_sid)])

write_csv(species_id_lookup, file.path(dir_git, 'data/species_id_lookup.csv'))
# length(species_id_lookup$iucn_sid %>% unique()); length(species_id_lookup$am_sid %>% unique())
### 2335 iucn_sid, 2335 am_sid

@@

species_id_lookup <- read_csv(file.path(dir_git, 'data/species_id_lookup.csv'))

spp_am_v_iucn <- spp_all %>%
  select(-iucn_subpop) %>%
  filter(iucn_sid %in% species_id_lookup$iucn_sid & am_sid %in% species_id_lookup$am_sid) %>% #  & !is.na(am_sid)) %>%
  unique()

# length(unique(spp_am_v_iucn$sciname)); length(unique(spp_am_v_iucn$am_sid)); length(unique(spp_am_v_iucn$iucn_sid))
### NOTE: 23325 unique scientific names, unique am_sid and unique iucn_sid.
### Seasnakes are included in Reptiles (IUCN).  Two "mangroves" that are actually seagrasses.
spp_am_v_iucn <- spp_am_v_iucn %>%
  group_by(am_sid, iucn_sid) %>%
  mutate(dupes = n() - 1) %>%
  ungroup() %>%
  filter(!(dupes == 1 & spp_group == 'MANGROVES')) %>%
  filter(spp_group != 'SEASNAKES') %>%
  select(-dupes)
# length(unique(spp_am_v_iucn$sciname)); length(unique(spp_am_v_iucn$am_sid)); length(unique(spp_am_v_iucn$iucn_sid))
### still same scinames and am_sid

sciname_dupes <- spp_am_v_iucn %>%
  group_by(am_sid) %>%
  filter(n() > 1)
### these seem to be spp with IUCN maps for synonyms.  Keep 'em in.

@@

spp_map_pairs <- read_csv(file.path(dir_data, 'spp_list_w_area_trimmed.csv'))

library(rgbif)

# system.time({
#   x <- occ_search(scientificName = spp_map_pairs$sciname, fields = 'minimal', limit = 1)
#   ### seems linear - 10 names ~ 2.5 sec, 100 names ~ 25 sec, 1000 names, ~250 sec
#   ### so 30000 names ~ 7500 sec or 2 hours
# })
# y <- sapply(x, function(x) x$meta$count) %>%
#   unlist()
# gbif_occur <- data.frame(sciname = names(y), gbif_occ = y)
# 
# gbif_occur <- spp_map_pairs %>%
#   select(iucn_sid, am_sid, sciname) %>%
#   left_join(gbif_occur,
#             by = 'sciname') %>%
#   left_join(read_csv(file.path(dir_data_remote, 'aquamaps/d2015/csv/speciesoccursum.csv')) %>%
#                        select(am_sid = speciesid, occurcells),
#                      by = 'am_sid')
# 
# # plot(gbif_occ ~ occurcells, data = gbif_occur)
# # print(summary(lm(obs ~ occurcells, data = gbif_occur)))
# 
# write_csv(gbif_occur, file.path(dir_data, 'gbif_occurrence.csv'))
# # gbif_occur <- read_csv(file.path(dir_data, 'gbif_occurrence.csv'))

# source('obis_count.R')
# scinames <- spp_map_pairs$sciname
# 
# obis_occur <- obis_count(scinames, verbose = TRUE)
# # obis_occur <- obis_count(scinames[1:10], verbose = TRUE)
# 
# obis_occur <- spp_map_pairs %>%
#   select(iucn_sid, am_sid, sciname) %>%
#   left_join(obis_occur,
#             by = 'sciname') %>%
#   left_join(read_csv(file.path(dir_data_remote, 'aquamaps/d2015/csv/speciesoccursum.csv')) %>%
#                        select(am_sid = speciesid, occurcells),
#                      by = 'am_sid')
# 
# write_csv(obis_occur, file.path(dir_data, 'obis_occurrence.csv'))
# # obis_occur <- read_csv(file.path(dir_data, 'obis_occurrence.csv'))

### 2017-04-21 shiny_am_iucn/data_prep.Rmd
initialize dummy branch

### copy and trim the list of overlapping species
spp_list_quads <- read_csv(file.path(dir_git, 'data', 'spp_list_quads.csv')) %>%
  select(sciname, iucn_sid, am_sid, 
         area_iucn, area_am,
         dist_align = sm_perc, area_ratio, 
         spp_group_text, 
         reviewed, occurcells, 
         n_spp, quad) %>%
  mutate(reviewed = ifelse(!is.na(reviewed), TRUE, FALSE))
write_csv(spp_list_quads, file.path(dir_shiny, 'data', 'spp_list_quads_app.csv'))

@@

### recalc areas and overlaps
iucn_coral_fixed <- spp_coralmaps %>%
  gather(dist, dist_align, c(sm_perc_raw, sm_perc_shallow)) %>%
  gather(area, area_ratio, c(area_ratio_raw, area_ratio_shallow)) %>%
  filter(!(str_detect(dist, 'raw') & !(str_detect(area, 'raw')))) %>%
  filter(!(str_detect(dist, 'shallow') & !(str_detect(area, 'shallow')))) %>%
  mutate(method = ifelse(str_detect(dist, 'shallow'), '200 m clip', 'all depth')) %>%
  select(iucn_sid, am_sid, sciname, dist_align, area_ratio, method) %>%
  distinct()

@@

coral_spp_list  <- spp_list %>%
  select(iucn_sid, sciname) %>%
  filter(iucn_sid %in% coral_cells_app$iucn_sid) %>%
  distinct()
write_csv(spp_coral_maps, file.path(dir_shiny, 'data', 'coral_spp_list.csv'))

>>>>

### copy and trim the list of overlapping species
comnames <- read_csv(file.path(dir_shiny, 'data/sci_to_common.csv'))

spp_list_quads <- read_csv(file.path(dir_git, 'data', 'spp_list_quads.csv')) %>%
  select(sciname, iucn_sid, am_sid, 
         area_iucn, area_am,
         dist_align = sm_perc, area_ratio, 
         spp_group_text, 
         reviewed, occurcells, 
         n_spp, quad) %>%
  left_join(comnames, by = 'sciname') %>%
  mutate(reviewed = ifelse(!is.na(reviewed), TRUE, FALSE),
         name = ifelse(is.na(common) | common == 'Null', sciname, common)) %>%
  select(-fbname)
write_csv(spp_list_quads, file.path(dir_shiny, 'data', 'spp_list_quads_app.csv'))

@@

comnames <- read_csv(file.path(dir_shiny, 'data', 'spp_list_quads_app.csv')) %>%
  dplyr::select(iucn_sid, sciname, name)

### recalc areas and overlaps
iucn_coral_fixed <- spp_coralmaps %>%
  gather(dist, dist_align, c(sm_perc_raw, sm_perc_shallow)) %>%
  gather(area, area_ratio, c(area_ratio_raw, area_ratio_shallow)) %>%
  filter(!(str_detect(dist, 'raw') & !(str_detect(area, 'raw')))) %>%
  filter(!(str_detect(dist, 'shallow') & !(str_detect(area, 'shallow')))) %>%
  mutate(method = ifelse(str_detect(dist, 'shallow'), '200 m clip', 'all depth')) %>%
  select(iucn_sid, am_sid, sciname, dist_align, area_ratio, method) %>%
  distinct() %>%
  left_join(comnames, by = c('iucn_sid', 'sciname'))

@@

coral_spp_list  <- spp_list %>%
  select(iucn_sid, sciname, name) %>%
  filter(iucn_sid %in% coral_cells_app$iucn_sid) %>%
  distinct()
write_csv(coral_spp_list, file.path(dir_shiny, 'data', 'coral_spp_list.csv'))
